\documentclass{article}

\usepackage{nips12submit_e, times}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bm}

% ======= Dai Wei's preambles. Please don't delete =======
\newcommand{\phib}{\bm{\phi}}
\newcommand{\vecu}[1]{\underline{\mathbf{#1}}}
\newcommand{\wb}{\mathbf{w}}
\newcommand{\xb}{\mathbf{x}}
\newcommand{\defeq}{\stackrel{\Delta}{=}}
\DeclareMathOperator*{\argmax}{arg\,max}
% ======= Dai Wei's preambles. Please don't delete =======

\title{An Empirical Study of Approximate Inference Algorithms on Bayesian
Logistic Regression}

\author{
Wei Dai \\
School of Computer Science \\
Carnegie Mellon University\\
Pittsburgh, PA 15213\\
\texttt{wdai@cs.cmu.edu}\\
\And
Abhimanu Kumar \\
School of Computer Science \\
Carnegie Mellon University\\
Pittsburgh, PA 15213\\
\texttt{abhimank@cs.cmu.edu}\\
\And
Jinliang Wei \\
School of Computer Science \\
Carnegie Mellon University\\
Pittsburgh, PA 15213\\
\texttt{jinlianw@cs.cmu.edu}\\
}
\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}
\nipsfinalcopy
\begin{document}
\maketitle

\begin{abstract}

With the recent development of analytically intractable graphical models, many
approximation inference algorithms such as variational inferences and sampling
techniques have also emerged. Despite a large body of studies on these
approximate methods, there is currently no clear comparison of their relative
performances on various models and datasets.  Here we present an empirical
study of Bayesian logistic regression using three variational methods and one
sampling algorithm.  With Guassian prior, Bayesian logistic regression is an
analytically intractable model and presents considerable challeges due to the
non-conjugacy between the Guassian prior and the sigmoid likelihood function.
We present clever techniques to handle the non-cnjugacy in variational as well
as sampling methods. We analyze the algorithms on three diverse datasets and
present run time results for speed comparison among the different
approximation techniques. Our results give convincing evidences that sampling
based method outperforms variational inferences but requires longer runtime
compared with variational inferences.  We hypothesize this difference between
variational inference and sampling method to be generalizable to other models
and datasets.

\end{abstract}

\setcounter{page}{1}
\pagenumbering{arabic}
% \vspace{-20pt}
% \section{Project Idea}
% \vspace{-5pt}

\input{intro}
\input{related_work}
\input{method}
\input{experiments}
\input{conclusion}



\bibliographystyle{plain}
\bibliography{reference}

\end{document}
